A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-03-16 doc/paper.tex
Some viz formatting work

Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts. Collections like EUSES[yada], FUSE[yada], and the Enron corpus[yada] have already enabled fruitful work across the field: [WORK PENDING MORE RESEARCH]. A number of these studies focus on discovering which built-in functions are the most common (enabling something). \par

@@

\section{Related Work}
Spreadsheets, being a core component of business that they are, have prompted the development of many tools to evaluate them and their many qualities. [RESEARCH ON NON-VISUAL ANALYSIS TOOLS] \par
Furthermore, this tool comes from a line of spreadsheet visualization tools before it, each with a different focus. For example, Breviz, developed by Hermans and colleagues, uses visualization to illustrate workbook dataflow to address the need for a clearly communicable representation of spreadsheets as they move from person to person. \par
Other studies focus on API and built-in function use outside the domain of spreadsheets. [BUT FIRST I HAVE TO FIND THEM]

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vivamus ultricies volutpat laoreet. Suspendisse tempus sapien metus, eget eleifend risus vehicula nec. Nulla facilisi. Aliquam non sapien ut tellus sagittis varius vel non nisl. Ut interdum nibh interdum odio ullamcorper, ac rhoncus leo tincidunt. Suspendisse potenti. Sed at scelerisque urna. Duis vehicula, nulla sed luctus aliquet, ante ante finibus arcu, at condimentum ante velit accumsan ligula. Sed suscipit, risus et blandit vestibulum, nibh felis mollis tellus, id pharetra nisi tellus sed augue. Cras nunc orci, semper auctor cursus sed, sodales eu risus. Etiam nec diam sed mi fringilla luctus sit amet quis neque.

Etiam porttitor lectus a augue volutpat suscipit. Pellentesque sodales dictum convallis. Cras varius pharetra tempor. Sed id finibus libero. Nullam aliquet posuere pellentesque. Sed rhoncus consequat lectus sed fermentum. Interdum et malesuada fames ac ante ipsum primis in faucibus. Fusce euismod justo non velit molestie, vitae efficitur dui molestie. Ut molestie eros ullamcorper, convallis nibh vel, varius libero. Nulla sit amet tincidunt risus, sed porta nisi. Phasellus faucibus ut nisl vitae convallis.

Nulla efficitur diam diam, ac aliquam sapien vestibulum nec. Aliquam eu tempus sem, placerat dapibus metus. Sed augue tortor, hendrerit vitae ex et, vestibulum placerat erat. Donec rhoncus scelerisque nunc, sed elementum ipsum pharetra scelerisque. In bibendum massa eros, tristique sodales justo placerat at. Praesent egestas convallis nunc, in tempor ex tempus at. Suspendisse potenti. Maecenas mi tortor, aliquet a nibh nec, pretium dignissim nunc. Nullam eleifend volutpat facilisis. In condimentum ut ante nec ullamcorper. Sed finibus cursus justo vel pharetra. Praesent elit odio, semper eget dolor eu, tempor tristique eros. Praesent dapibus nec velit at aliquet.

Sed a tempor velit. Maecenas congue consectetur elementum. Vestibulum dolor ante, aliquet et augue sed, congue vestibulum ligula. Vivamus viverra ex quis justo varius sodales. Nulla finibus risus vitae orci porta, a ornare ex aliquet. Sed mi sapien, sollicitudin tempus justo vitae, eleifend auctor sem. Aliquam aliquam purus quam.

In rutrum tortor et enim fringilla, in dictum dui vulputate. Maecenas ut ligula et ipsum euismod ornare ut vel eros. Duis sit amet urna in tortor pretium convallis. Morbi vitae sollicitudin nisl. Etiam semper urna a ex aliquam malesuada. Aenean non bibendum velit, eu auctor metus. Integer vestibulum id turpis eget mattis. Donec diam nisi, rhoncus bibendum sollicitudin sed, eleifend vel massa. Curabitur ut ornare felis. Nullam viverra nulla in suscipit facilisis. Quisque mollis turpis id massa mattis sagittis. Ut vitae arcu a lectus gravida varius. Ut porttitor auctor rhoncus.

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Fusce tristique lobortis euismod. Suspendisse dapibus ultrices bibendum. Etiam accumsan augue metus, sit amet accumsan dui tempus eu. Donec sed nibh id tellus posuere luctus. Ut vel sagittis tellus. Phasellus dapibus pharetra nibh a consectetur. Phasellus dignissim nibh posuere, auctor mauris eu, vestibulum nulla. Aliquam mi nibh, maximus vel interdum non, molestie vitae ante. Donec vitae lacinia purus, eget maximus leo. Duis volutpat congue ligula non hendrerit.

Donec ac nibh imperdiet, hendrerit mi ac, viverra dolor. Vivamus tincidunt vehicula aliquet. In mollis egestas justo vel tincidunt. Donec in efficitur nisl. Donec eu nisl eu sem mattis malesuada et vitae lorem. Morbi urna purus, consectetur eget enim eget, interdum tincidunt diam. Etiam ultrices, metus nec fermentum porta, eros augue faucibus mauris, vitae ultricies nulla urna eget eros. Ut egestas, lorem ac volutpat pretium, est sem iaculis augue, et congue nisl massa vitae ipsum. Nulla facilisi. Donec metus nibh, laoreet et finibus ut, pretium eu ante. Fusce mauris enim, interdum nec consequat ac, interdum vitae ipsum. Mauris malesuada vitae arcu eu sagittis. Nullam euismod purus arcu, vitae consequat erat efficitur eu. Donec egestas felis sed mauris sagittis, at sodales neque lobortis.

Curabitur sed ultricies nisi. Sed pharetra non dui nec dapibus. Sed tincidunt lacinia mi at elementum. Suspendisse egestas risus scelerisque viverra vestibulum. In hac habitasse platea dictumst. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Donec fermentum libero eget libero iaculis porttitor. Curabitur libero nisl, varius ac lorem vel, ornare viverra erat. Nunc id magna est. Integer interdum tristique nulla, nec mattis nisl hendrerit a. Quisque turpis nisl, feugiat in sagittis a, viverra at massa.

>>>>

Fortunately, the vanguards of spreadsheet research have assembled, organized, and released a number of spreadsheet corpora to inform work on how people actually use these tools in different contexts. Collections like EUSES[cite], FUSE[cite], and the Enron corpus[cite] have already enabled fruitful work across the field: [EXAMPLES FROM RESEARCH]. A number of these studies focus on discovering which built-in functions are the most common (enabling something). \par

@@

\section{Related Work}
Spreadsheets, being a core component of business that they are, have prompted the development of many tools to evaluate them and their many qualities. [RESEARCH ON NON-VISUAL ANALYSIS TOOLS] \par
Furthermore, this tool comes from a line of spreadsheet visualization tools before it, each with a different focus. For example, Breviz, developed by Hermans and colleagues, uses visualization to illustrate workbook dataflow to address the need for a clearly communicable representation of spreadsheets as they move from person to person. \par
Other studies focus on API and built-in function use outside the domain of spreadsheets. [RESEARCH ON API STUDIES]

@@

[to be filled in]

@@

[to be filled in]
